\LARGE \bf Cross Validation of Emotional Features with a non-Anthropomorphic Platform

### 2017-03-23 RO-MAN-2017-1/Parts/CaseStudy.tex
Update CaseStudy.tex

 The case study presented in this paper was held at an exhibition with two main objectives:
\begin{enumerate}
	\item Cross-validate the findings obtained from a previous experiment~\cite{Angel2017-2}. This experiment was done to study the attribution of different linear and angular velocities, oscillation angle, direction, and orientation of the platform to \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}. A total of 196 value combinations were designed, 20 of which were presented to each participant. Subjects had to select for each presentation the most representative term describing it among the four emotions and two mental states (i.e., \textit{Excitement} and \textit{Tenderness}).
	\item Verify whether participants would prefer scenes when the robot moves expressing emotions or rather moves on the same trajectory without any emotion expression. To control scene variability two cameras and eight AR tags were used together with a Kalman filter to improve robot localization on the stage. AR tags were detected using the ROS package ar\_track\_alvar~\cite{artag2015}. The distribution of thecameras and the tags is reported in Figure~\ref{fig:setup_fourth}.

@@

Stage discretization was used to give zones of movements instead of absolute positions. This idea was brought from human theatrical actors, who arrange their movements based on zones on the stage~\cite{wilson2009theatre}. This allows them to adapt their position based on other actors and stage dimensions. The stage was discretized in 9x9 matrix as shown in Figure~\ref{fig:stage_division}. Robot's movements are given in terms of matrix positions to the Emotional Enrichment System. The robot's final position is calculated by the Emotional Enrichment System during execution. For instance, the scene was designed on a 3 x 3 meters stage, but in the presentation at the exhibition the stage was 2.5 x 2.5 meters.

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{./Images/FourthCaseScene.png} 
	\caption{Stage discretization  used for the scene. The blue squares correspond to the each zone, while the numbers correspond to the ID given to each zone.}
	\label{fig:stage_division}
\end{figure}

@@

This case study was done at an exhibition during a period of two days. People coming to the stand were asked to participate in this study, which was divided in to parts. In the first one, each subject was exposed to two emotion expressions. %TODO Was it so? I have turned the sentence... 
The two emotions were generated to guarantee a random uniform presentation. In the second part, participants were explained that a small scene was going to be presented twice, and they had to select the one they like more. The order of the scenes (e.g., with or without emotion) was generated beforehand. The total number of volunteers was 256: 128 males, 126 females, and 2 that chose not to specify their gender. The average age was 27.29 years, with standard deviation of 16.58, minimum age was 4 and maximum 76. We accepted this variability as representative of a general population.

>>>>

 The case study presented in this paper was held at an exhibition with two main objectives:
\begin{enumerate}
	\item Cross-validate the findings obtained from a previous experiment~\cite{Angel2017-2}, which was done to study the attribution of different linear and angular velocities, oscillation angle, direction, and orientation of the platform to express: \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}. A total of 196 value combinations were designed, 20 of which, randomly selected, were presented to each participant. Subjects had to select for each presentation the most representative term describing it among the four emotions and two mental states (i.e., \textit{Excitement} and \textit{Tenderness}), added as confounding terms.
	\item Verify whether participants would prefer scenes where the robot moves expressing emotions, or rather moves on the same trajectory without any emotion expression. To control scene variability two cameras and eight AR tags were used together with a Kalman filter to improve robot localization on the stage. AR tags were detected using the ROS package ar\_track\_alvar~\cite{artag2015}. The distribution of the cameras and the tags is reported in Figure~\ref{fig:setup_fourth}.

@@

Stage discretization was used to give zones of movement instead of absolute positions. This idea was brought from human theatrical actors, who arrange their movements based on zones on the stage~\cite{wilson2009theatre}. This allows them to adapt their position based on other actors and stage dimensions. The stage was discretized in 9x9 matrix as shown in Figure~\ref{fig:stage_division}. Robot's movements are given in terms of matrix positions to the Emotional Enrichment System. The robot's final position is calculated by the Emotional Enrichment System during execution. In this setting, the scene was designed on a 3 x 3 meters stage, but in the presentation at the exhibition the stage was 2.5 x 2.5 meters.

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{./Images/FourthCaseScene.png} 
	\caption{Stage discretization  used for the scene. The dark squares correspond to the each zone, while the numbers correspond to the ID given to each zone.}
	\label{fig:stage_division}
\end{figure}

@@

This case study was done at an exhibition during a period of two days. People coming to the stand were asked to volunteerto participate in this study, which was divided in to parts. In the first one, each subject was exposed to two emotion expressions. %TODO Was it so? I have turned the sentence... 
The two emotions were generated to guarantee a random uniform presentation. In the second part, participants were explained that a small scene was going to be presented twice, and they had to select the one they like more. The order of the scenes (e.g., with or without emotion) was generated beforehand. The total number of volunteers was 256: 128 males, 126 females, and 2 that chose not to specify their gender. The average age was 27.29 years, with standard deviation of 16.58, minimum age was 4 and maximum 76. We accepted this variability as representative of a general population.
